Case study validations of automatic bullet matching

### 2018-11-21 index.Rmd
remove unnecessary comment
compile separate title page when document is compiled

@@

\svp{XXX Should we have some sort of header here to differentiate it from the previous section?}

>>>>

```{r child-doc-compile, include = F}
library(stringr)
thisdoc <- readLines("index.Rmd")
idxs <- which(thisdoc == "---")
if (length(idxs) >= 2) {
  # Get yaml metadata, set to nonblinded, write to title-page.Rmd
  thisdoc[idxs[1]:idxs[2]] %>%
    str_replace("^blinded: 1", "blinded: 0") %>%
    writeLines(con = "title-page.Rmd")
}

rmarkdown::render("title-page.Rmd", clean = T)
```

@@
